Paper Codes

### 2024-04-26 paper_codes.Rmd
final changes

Netherlands boundary shapefile
Coordinates are in EPSG:28992, the Projected coordinate system for Netherlands. These coordinates are calculated from the center of the Netherlands in meters. For simplicity, we convert them to kilometers below.

@@

Data for vegetation plots and abiotic measurements data
Coordinates are in EPSG:28992, the Projected coordinate system for Netherlands.

@@

Data for Netherlands grid
Coordinates are in EPSG:28992, the Projected coordinate system for Netherlands.

@@

```{r}
ggplot(NL) + geom_sf() +
	geom_sf(aes(geometry=geometry.1, fill=landuse), data=sf.grid) +
  scale_fill_manual(values=c("Forest"="forestgreen", "Built"="slategrey",
                             "Natural terrain (dry)"="peru","Natural terrain (wet)"="lightseagreen",
                             "Highway"="grey","Railway"="seashell2", "Agricultural"="wheat",#
                             "Recreatie"="lawngreen", "Water"="dodgerblue"
                             )) +
	theme(legend.position="right") #+ggtitle('Grid of Netherlands: Landuse') 
ggsave('results_paper/landuse.png', width=1600, heigh=1200, units='px')
```

@@

ggplot(data=f, aes(x=Var1, y=Freq, fill=Data)) +
  geom_bar(stat="identity", position=position_dodge()) +
  scale_fill_manual(values=c('#999999','#E69F00')) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  xlab('Landuse') + ylab('% of total') #+ ggtitle('Landuse: Grid of Netherlands vs. Field visits')
ggsave('results_paper/landuse_vs_visit.png', width=1400, heigh=900, units='px')
```

@@

```{r}
ggplot(NL) + geom_sf() +
	geom_sf(aes(geometry=geometry.1), data=sf.grid) + 
	#geom_sf(aes(geometry=geometry), shape=3, size=0.3, data=sf.grid) + 
	geom_sf(aes(geometry=geometry, color=has_abiotics), shape=4, size=0.5, data=sf.plots) + 
	theme(plot.title = element_text(hjust = 0.5), legend.title=element_text(size=10), 
		legend.text=element_text(size=8), legend.position="right") +
	scale_colour_manual(values=c("#377EB8", "#4DAF4A"), name="Has abiotics") #+ 
	#ggtitle('Location of Field Visits and Abiotics') 
ggsave('results_paper/visits.png', width=1400, heigh=1200, units='px')

@@

plot_grid(plot1, plot2, nrow = 1)
ggsave('results_paper/Struikhei.png', width=2000, heigh=1400, units='px')
```

@@

plot.all <- ggdraw() +
  draw_plot(plot1, x = 0, y = 0, width = 0.50, height = 0.95) +
  draw_plot(plot2, x = 0.50, y = 0, width = 0.50, height = 0.95) +
  draw_plot_label(label = c("A", "B"), size = 15, x = c(0.01, 0.50), y = c(0.99,0.99)) +
  theme(plot.background = element_rect(fill = "white", colour = NA))
plot.all
ggsave('results_paper/pH.png', width=2000, heigh=1400, units='px')
```

@@

```{r}
plot3 <- ggplot(NL) + geom_sf() + geom_sf(aes(geometry=geometry.1, fill=pH.sd), data=results) + 
  scale_fill_gradient(low='white', high='red', limits=c(0,1.11)) + ggtitle('Uncertainty pH') + theme(legend.position="bottom")
plot_grid(plot1, plot2, plot3, nrow = 1) + theme(plot.background = element_rect(fill = "white", colour = NA)) #, plot3
ggsave('results_paper/pH2.png', width=3000, heigh=1400, units='px')
```

@@

## Experiments: training and validation
It is also possible to download the results from https://zenodo.org/record/8261504
In that case, place the downloaded files in the subfolder `data_paper/` and go to the `Results: import file` section below to import the results and create the plots.

@@

Combine and export the results of fitting all models to data: 
It is also possible to skip this cell and download the results from https://zenodo.org/record/8261504
Place the data in the subfolder `data_paper/` and run the code below this cell to create the plots.

@@

## Results: import file

@@

## Results: crowberry example

@@

```{r}
plot.all <- ggdraw() +
  draw_plot(plot.splines, x = 0, y = .666, width = 1, height = .333) +
  draw_plot(plot.abiotic + theme(legend.position = "none"), x = 0, y = .333, width = .77, height = .333) +
  draw_plot(plot.spatial + theme(legend.position = "none"), x = 0.77, y = .333, width = 0.23, height = 0.333) +
  draw_plot(plot.extrapolate + theme(legend.position = "none"), x = 0, y = 0, width = 1, height = 0.333) +
  draw_plot_label(label = c("A", "B", "C", "D"), size = 15, x = c(0.03, 0.03, 0.79, 0.03), y = c(0.96, 0.70, 0.70, 0.37))
plot.all
ggsave('results_paper/species_parameters.png', width=2000, heigh=2500, units='px')
```

@@

plot0 <- ggplot(NL) + geom_sf() + geom_sf(aes(fill=y), data=terms.sf %>% filter(meta=="Uncertain")) + 
  scale_fill_viridis_c(option="B", limits=c(0,1)) + ggtitle("Raw data") + 
  theme(legend.position="bottom", legend.key.width = unit(0.06, "npc"))
plot1 <- ggplot(NL) + geom_sf() + geom_sf(aes(fill=mean), data=terms.sf %>% filter(meta=="Uncertain")) + 
  scale_fill_viridis_c(option="B", limits=c(0,1)) + ggtitle("Joint Model") + 
  theme(legend.position="bottom", legend.key.width = unit(0.06, "npc"))
plot2 <- ggplot(NL) + geom_sf() + geom_sf(aes(fill=mean), data=terms.sf %>% filter(meta=="Certain")) + 
  scale_fill_viridis_c(option="B", limits=c(0,1)) + ggtitle("Two-Stage Model") + 
  theme(legend.position="bottom", legend.key.width = unit(0.06, "npc"))
plot4 <- ggplot(NL) + geom_sf() + geom_sf(aes(fill=sd), data=terms.sf %>% filter(meta=="Uncertain")) + 
  scale_fill_gradient(low='darkblue', high='yellow', limits=c(0,max(terms.sf$sd))) + ggtitle("Joint Model") + 
  theme(legend.position="bottom", legend.key.width = unit(0.06, "npc"))
plot5 <- ggplot(NL) + geom_sf() + geom_sf(aes(fill=sd), data=terms.sf %>% filter(meta=="Certain")) + 
  scale_fill_gradient(low='darkblue', high='yellow', limits=c(0,max(terms.sf$sd))) + ggtitle("Two-Stage Model") + 
  theme(legend.position="bottom", legend.key.width = unit(0.06, "npc"))
#plot.all <- plot_grid(plot0, plot1, plot2, NULL, plot4, plot5, nrow = 2) + theme(plot.background = element_rect(fill = "white", colour = NA))
plot.all <- ggdraw() +
  draw_plot(plot0, x = 0, y = .5, width = 0.33, height = .5) +
  draw_plot(plot1, x = 0.33, y = .5, width = 0.33, height = .5) +
  draw_plot(plot2, x = 0.66, y = .5, width = 0.33, height = .5) +
  draw_plot(plot4, x = 0.33, y = 0, width = 0.33, height = .5) +
  draw_plot(plot5, x = 0.66, y = 0, width = 0.33, height = .5) +
  draw_plot_label(label = c("A", "B", "C", "D", "E"), size = 15, x = c(0.00, 0.33, 0.66, 0.33, 0.66), y = c(1.00, 1.00, 1.00, 0.50, 0.50))
plot.all
ggsave('results_paper/species_SDM_y.png', width=3200, heigh=3000, units='px')
```

@@

plot0 <- ggplot(NL) + geom_sf() + geom_sf(aes(fill=y), data=terms.sf %>% filter(meta=="Uncertain")) + 
  scale_fill_viridis_c(option="B", limits=c(0,1)) + ggtitle("Raw data") + 
  theme(legend.position="bottom", legend.key.width = unit(0.06, "npc"))
plot1 <- ggplot(NL) + geom_sf() + geom_sf(aes(fill=mean), data=terms.sf %>% filter(meta=="Uncertain")) + 
  scale_fill_continuous_divergingx(palette = 'PiYG', mid = y.mean) + ggtitle("Joint Model") + 
  theme(legend.position="bottom", legend.key.width = unit(0.06, "npc"))
plot2 <- ggplot(NL) + geom_sf() + geom_sf(aes(fill=mean), data=terms.sf %>% filter(meta=="Certain")) + 
  scale_fill_continuous_divergingx(palette = 'PiYG', mid = y.mean) + ggtitle("Two-Stage Model") + 
  theme(legend.position="bottom", legend.key.width = unit(0.06, "npc"))
plot4 <- ggplot(NL) + geom_sf() + geom_sf(aes(fill=sd), data=terms.sf %>% filter(meta=="Uncertain")) + 
  scale_fill_gradient(low='darkblue', high='orange', limits=c(0,max(terms.sf$sd))) + ggtitle("Joint Model") + 
  theme(legend.position="bottom", legend.key.width = unit(0.06, "npc"))
plot5 <- ggplot(NL) + geom_sf() + geom_sf(aes(fill=sd), data=terms.sf %>% filter(meta=="Certain")) + 
  scale_fill_gradient(low='darkblue', high='orange', limits=c(0,max(terms.sf$sd))) + ggtitle("Two-Stage Model") + 
  theme(legend.position="bottom", legend.key.width = unit(0.06, "npc"))
#plot.all <- plot_grid(plot0, plot1, plot2, NULL, plot4, plot5, nrow = 2) + theme(plot.background = element_rect(fill = "white", colour = NA))
plot.all <- ggdraw() +
  draw_plot(plot0, x = 0, y = .5, width = 0.33, height = .5) +
  draw_plot(plot1, x = 0.33, y = .5, width = 0.33, height = .5) +
  draw_plot(plot2, x = 0.66, y = .5, width = 0.33, height = .5) +
  draw_plot(plot4, x = 0.33, y = 0, width = 0.33, height = .5) +
  draw_plot(plot5, x = 0.66, y = 0, width = 0.33, height = .5) +
  draw_plot_label(label = c("A", "B", "C", "D", "E"), size = 15, x = c(0.00, 0.33, 0.66, 0.33, 0.66), y = c(1.00, 1.00, 1.00, 0.50, 0.50))
plot.all
ggsave('results_paper/species_SDM_logodds.png', width=3200, heigh=3000, units='px')

@@

plot0 <- ggplot(NL) + geom_sf() + geom_sf(aes(fill=y), data=terms.sf %>% filter(meta=="Uncertain")) + 
  scale_fill_gradient2(low='blue', midpoint=0, high='red', limits=c(-3,3)) + 
  ggtitle(sprintf('Raw data %s', var)) + theme(legend.position="bottom", legend.key.width = unit(0.06, "npc"))
plot1 <- ggplot(NL) + geom_sf() + geom_sf(aes(fill=mean), data=terms.sf %>% filter(meta=="Uncertain")) + 
  scale_fill_gradient2(low='blue', midpoint=0, high='red', limits=c(-3,3)) + 
  ggtitle(sprintf('Joint Model %s', var)) + theme(legend.position="bottom", legend.key.width = unit(0.06, "npc"))
plot2 <- ggplot(NL) + geom_sf() + geom_sf(aes(fill=mean), data=terms.sf %>% filter(meta=="Certain")) + 
  scale_fill_gradient2(low='blue', midpoint=0, high='red', limits=c(-3,3)) + 
  ggtitle(sprintf('Two-Stage Model %s', var)) + theme(legend.position="bottom", legend.key.width = unit(0.06, "npc"))
plot4 <- ggplot(NL) + geom_sf() + geom_sf(aes(fill=sd), data=terms.sf %>% filter(meta=="Uncertain")) + 
  scale_fill_gradient(low='white', high='red', limits=c(0,max(terms.sf$sd))) + 
  ggtitle(sprintf('Joint Model %s', var)) + theme(legend.position="bottom", legend.key.width = unit(0.06, "npc"))
plot5 <- ggplot(NL) + geom_sf() + geom_sf(aes(fill=sd), data=terms.sf %>% filter(meta=="Certain")) + 
  scale_fill_gradient(low='white', high='red', limits=c(0,max(terms.sf$sd))) + 
  ggtitle(sprintf('Two-Stage Model %s', var)) + theme(legend.position="bottom", legend.key.width = unit(0.06, "npc"))
#plot.all <- plot_grid(plot0, plot1, plot2, NULL, plot4, plot5, nrow = 2) + theme(plot.background = element_rect(fill = "white", colour = NA))
plot.all <- ggdraw() +
  draw_plot(plot0, x = 0, y = .5, width = 0.33, height = .5) +
  draw_plot(plot1, x = 0.33, y = .5, width = 0.33, height = .5) +
  draw_plot(plot2, x = 0.66, y = .5, width = 0.33, height = .5) +
  draw_plot(plot4, x = 0.33, y = 0, width = 0.33, height = .5) +
  draw_plot(plot5, x = 0.66, y = 0, width = 0.33, height = .5) +
  draw_plot_label(label = c("A", "B", "C", "D", "E"), size = 15, x = c(0.00, 0.33, 0.66, 0.33, 0.66), y = c(1.00, 1.00, 1.00, 0.50, 0.50))
ggsave(sprintf('results_paper/species_%s.png', var), width=3200, heigh=3000, units='px')
}
```

@@

plot.scatter <- ggplot() + geom_point(aes(x=`Two-Stage Model`, y=`Joint Model`), data=terms.plot, size=0.1, alpha=0.2) + geom_abline() + 
     facet_wrap( ~ type + model, ncol = 3, scales="free") #+ ggtitle('Predicted Log-Odds (SDM) and \nPredicted Mean (Abiotics) at Grid Cells')
plot.scatter
ggsave('results_paper/species_scatter.png', width=1800, heigh=2400, units='px')
```

@@

@@

```{r}
# Linear terms for all species
terms.plot <- results %>% filter((term == "fixed") & (model == "SDM")  & (ID != "intercept")) %>% 
  mutate(ID=fct_relevel(ID, "ORG_STOF.z", "CN.z", "N_totaal.z", "P_totaal.z", "K_CaCl2.z")) %>% #"intercept",  
  mutate(meta=factor(recode(meta, "Certain" = "Two-Stage", "Uncertain"="Joint"), levels=c("Two-Stage", "Joint"))) %>%
  merge(species.map) %>% mutate(species = name)
plot.abiotics.all <- ggplot(terms.plot, aes(x=ID, y=mean, col=meta, group=meta)) + 
  geom_point(position=position_dodge(width=0.5), size=2) +
  geom_errorbar(position=position_dodge(width=0.5), aes(ymin=X0.025quant, ymax=X0.975quant)) +
  theme(legend.position="top", axis.text.x = element_text(angle = 90)) + 
  scale_color_discrete(name = "Model") +
  scale_x_discrete(name='Covariate') + 
  scale_y_continuous(name='Value') +coord_cartesian(ylim=c(-5,5))+ #ylim=c(-10,10)
  facet_wrap( ~ species, ncol = 5)#, scales="free"
plot.abiotics.all
ggsave('results_paper/all_abiotics.png', width=2400, heigh=4000, units='px')
```

@@

ggplot(compare.cor, aes(x=cor)) + 
  geom_histogram(color="black", fill="white", breaks=seq(0.8,1.0,0.01)) + 
  ylab("Number of Species") +xlab("Pearson Correlation Coefficient") +
  facet_wrap( ~ model, ncol = 3)  #+ggtitle('Correlation between Certain vs. Uncertain Abiotic Model Predictions')
ggsave('results_paper/species_correlation.png', width=2000, heigh=1200, units='px')

@@

>>>>

Netherlands boundary shapefile
Coordinates are in EPSG:28992, the Projected coordinate system for Netherlands. These coordinates are calculated from the center of the Netherlands in meters. We convert them to kilometers from the center below.

@@

Data for vegetation plots and abiotic measurements data

@@

Data for Netherlands grid

@@

```{r}
ggplot(NL) + geom_sf() +
	geom_sf(aes(geometry=geometry.1, fill=landuse), data=sf.grid) +
  scale_fill_manual(values=c("Forest"="forestgreen", "Built"="slategrey",
                             "Natural terrain (dry)"="peru","Natural terrain (wet)"="lightseagreen",
                             "Highway"="grey","Railway"="seashell2", "Agricultural"="wheat",#
                             "Recreatie"="lawngreen", "Water"="dodgerblue"
                             )) +
	theme(legend.position="right") #+ggtitle('Grid of Netherlands: Landuse') 
ggsave('results_paper/landuse.png', width=1600, heigh=1200, units='px')
ggsave('results_paper/landuse.tiff', width=1600, heigh=1200, units='px', compression="lzw")

@@

ggplot(data=f, aes(x=Var1, y=Freq, fill=Data)) +
  geom_bar(stat="identity", position=position_dodge()) +
  scale_fill_manual(values=c('#999999','#E69F00')) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  xlab('Landuse') + ylab('% of total') #+ ggtitle('Landuse: Grid of Netherlands vs. Field visits')
ggsave('results_paper/landuse_vs_visit.png', width=1400, heigh=900, units='px')
ggsave('results_paper/landuse_vs_visit.tiff', width=1400, heigh=900, units='px', compression="lzw")
```

@@

```{r}
ggplot(NL) + geom_sf() +
	geom_sf(aes(geometry=geometry.1), data=sf.grid) + 
	#geom_sf(aes(geometry=geometry), shape=3, size=0.3, data=sf.grid) + 
	geom_sf(aes(geometry=geometry, color=has_abiotics), shape=4, size=0.5, 
	        data=sf.plots %>% arrange(has_abiotics)) + 
	theme(plot.title = element_text(hjust = 0.5), legend.title=element_text(size=10), 
		legend.text=element_text(size=8), legend.position="right") +
	scale_colour_manual(values=c("#377EB8", "#4DAF4A"), name="Abiotic measurements") +
  scale_fill_discrete(guide=guide_legend(reverse=T))
	#ggtitle('Location of Field Visits and Abiotics') 
ggsave('results_paper/visits.png', width=1400, heigh=1200, units='px')
ggsave('results_paper/visits.tiff', width=1400, heigh=1200, units='px', compression="lzw")
```

@@

plot_grid(plot1, plot2, nrow = 1)
ggsave('results_paper/Struikhei.png', width=2000, heigh=1400, units='px')
ggsave('results_paper/Struikhei.tiff', width=2000, heigh=1400, units='px', compression="lzw")
```

@@

plot.all <- ggdraw() +
  draw_plot(plot1, x = 0, y = 0, width = 0.50, height = 0.95) +
  draw_plot(plot2, x = 0.50, y = 0, width = 0.50, height = 0.95) +
  draw_plot_label(label = c("A", "B"), size = 15, x = c(0.01, 0.50), y = c(0.99,0.99)) +
  theme(plot.background = element_rect(fill = "white", colour = NA))
plot.all
ggsave('results_paper/pH.png', width=2000, heigh=1400, units='px')
ggsave('results_paper/pH.tiff', width=2000, heigh=1400, units='px', compression="lzw")
```

@@

```{r}
plot3 <- ggplot(NL) + geom_sf() + geom_sf(aes(geometry=geometry.1, fill=pH.sd), data=results) + 
  scale_fill_gradient(low='white', high='red', limits=c(0,1.11)) + ggtitle('Uncertainty pH') + theme(legend.position="bottom")
plot_grid(plot1, plot2, plot3, nrow = 1) + theme(plot.background = element_rect(fill = "white", colour = NA)) #, plot3
ggsave('results_paper/pH2.png', width=3000, heigh=1400, units='px')
ggsave('results_paper/pH2.tiff', width=3000, heigh=1400, units='px', compression="lzw")
```

@@

## Experiments: training and validation

@@

Combine and export the results of fitting all models to data:

@@

## Results

It is also possible to download the results from https://zenodo.org/record/8261504
Place the data in the subfolder `data_paper/` and run the code below this cell.

@@

## Crowberry example

@@

```{r}
plot.all <- ggdraw() +
  draw_plot(plot.splines, x = 0, y = .666, width = 1, height = .333) +
  draw_plot(plot.abiotic + theme(legend.position = "none"), x = 0, y = .333, width = .77, height = .333) +
  draw_plot(plot.spatial + theme(legend.position = "none"), x = 0.77, y = .333, width = 0.23, height = 0.333) +
  draw_plot(plot.extrapolate + theme(legend.position = "none"), x = 0, y = 0, width = 1, height = 0.333) +
  draw_plot_label(label = c("A", "B", "C", "D"), size = 15, x = c(0.03, 0.03, 0.79, 0.03), y = c(0.96, 0.70, 0.70, 0.37))
plot.all
ggsave('results_paper/species_parameters.png', width=2000, heigh=2500, units='px')
ggsave('results_paper/species_parameters.tiff', width=2000, heigh=2500, units='px', compression="lzw")
```

@@

plot0 <- ggplot(NL) + geom_sf() + geom_sf(aes(fill=y), data=terms.sf %>% filter(meta=="Uncertain")) + 
  scale_fill_viridis_c(option="B", limits=c(0,1)) + ggtitle("Raw data") + 
  theme(legend.position="bottom", legend.key.width = unit(0.06, "npc"))
plot1 <- ggplot(NL) + geom_sf() + geom_sf(aes(fill=mean), data=terms.sf %>% filter(meta=="Uncertain")) + 
  scale_fill_viridis_c(option="B", limits=c(0,1)) + ggtitle("Joint Model") + 
  theme(legend.position="bottom", legend.key.width = unit(0.06, "npc"))
plot2 <- ggplot(NL) + geom_sf() + geom_sf(aes(fill=mean), data=terms.sf %>% filter(meta=="Certain")) + 
  scale_fill_viridis_c(option="B", limits=c(0,1)) + ggtitle("Two-Stage Model") + 
  theme(legend.position="bottom", legend.key.width = unit(0.06, "npc"))
plot4 <- ggplot(NL) + geom_sf() + geom_sf(aes(fill=sd), data=terms.sf %>% filter(meta=="Uncertain")) + 
  scale_fill_gradient(low='darkblue', high='yellow', limits=c(0,max(terms.sf$sd))) + ggtitle("Joint Model") + 
  theme(legend.position="bottom", legend.key.width = unit(0.06, "npc"))
plot5 <- ggplot(NL) + geom_sf() + geom_sf(aes(fill=sd), data=terms.sf %>% filter(meta=="Certain")) + 
  scale_fill_gradient(low='darkblue', high='yellow', limits=c(0,max(terms.sf$sd))) + ggtitle("Two-Stage Model") + 
  theme(legend.position="bottom", legend.key.width = unit(0.06, "npc"))
#plot.all <- plot_grid(plot0, plot1, plot2, NULL, plot4, plot5, nrow = 2) + theme(plot.background = element_rect(fill = "white", colour = NA))
plot.all <- ggdraw() +
  draw_plot(plot0, x = 0, y = .5, width = 0.33, height = .5) +
  draw_plot(plot1, x = 0.33, y = .5, width = 0.33, height = .5) +
  draw_plot(plot2, x = 0.66, y = .5, width = 0.33, height = .5) +
  draw_plot(plot4, x = 0.33, y = 0, width = 0.33, height = .5) +
  draw_plot(plot5, x = 0.66, y = 0, width = 0.33, height = .5) +
  draw_plot_label(label = c("A", "B", "C", "D", "E"), size = 15, x = c(0.00, 0.33, 0.66, 0.33, 0.66), y = c(1.00, 1.00, 1.00, 0.50, 0.50))
plot.all
ggsave('results_paper/species_SDM_y.png', width=3200, heigh=3000, units='px')
ggsave('results_paper/species_SDM_y.tiff', width=3200, heigh=3000, units='px', compression="lzw")
```

@@

plot0 <- ggplot(NL) + geom_sf() + geom_sf(aes(fill=y), data=terms.sf %>% filter(meta=="Uncertain")) + 
  scale_fill_viridis_c(option="B", limits=c(0,1)) + ggtitle("Raw data") + 
  theme(legend.position="bottom", legend.key.width = unit(0.06, "npc"))
plot1 <- ggplot(NL) + geom_sf() + geom_sf(aes(fill=mean), data=terms.sf %>% filter(meta=="Uncertain")) + 
  scale_fill_continuous_divergingx(palette = 'PiYG', mid = y.mean) + ggtitle("Joint Model") + 
  theme(legend.position="bottom", legend.key.width = unit(0.06, "npc"))
plot2 <- ggplot(NL) + geom_sf() + geom_sf(aes(fill=mean), data=terms.sf %>% filter(meta=="Certain")) + 
  scale_fill_continuous_divergingx(palette = 'PiYG', mid = y.mean) + ggtitle("Two-Stage Model") + 
  theme(legend.position="bottom", legend.key.width = unit(0.06, "npc"))
plot4 <- ggplot(NL) + geom_sf() + geom_sf(aes(fill=sd), data=terms.sf %>% filter(meta=="Uncertain")) + 
  scale_fill_gradient(low='darkblue', high='orange', limits=c(0,max(terms.sf$sd))) + ggtitle("Joint Model") + 
  theme(legend.position="bottom", legend.key.width = unit(0.06, "npc"))
plot5 <- ggplot(NL) + geom_sf() + geom_sf(aes(fill=sd), data=terms.sf %>% filter(meta=="Certain")) + 
  scale_fill_gradient(low='darkblue', high='orange', limits=c(0,max(terms.sf$sd))) + ggtitle("Two-Stage Model") + 
  theme(legend.position="bottom", legend.key.width = unit(0.06, "npc"))
#plot.all <- plot_grid(plot0, plot1, plot2, NULL, plot4, plot5, nrow = 2) + theme(plot.background = element_rect(fill = "white", colour = NA))
plot.all <- ggdraw() +
  draw_plot(plot0, x = 0, y = .5, width = 0.33, height = .5) +
  draw_plot(plot1, x = 0.33, y = .5, width = 0.33, height = .5) +
  draw_plot(plot2, x = 0.66, y = .5, width = 0.33, height = .5) +
  draw_plot(plot4, x = 0.33, y = 0, width = 0.33, height = .5) +
  draw_plot(plot5, x = 0.66, y = 0, width = 0.33, height = .5) +
  draw_plot_label(label = c("A", "B", "C", "D", "E"), size = 15, x = c(0.00, 0.33, 0.66, 0.33, 0.66), y = c(1.00, 1.00, 1.00, 0.50, 0.50))
plot.all
ggsave('results_paper/species_SDM_logodds.png', width=3200, heigh=3000, units='px')
ggsave('results_paper/species_SDM_logodds.tiff', width=3200, heigh=3000, units='px', compression="lzw")
```

@@

plot0 <- ggplot(NL) + geom_sf() + geom_sf(aes(fill=y), data=terms.sf %>% filter(meta=="Uncertain")) + 
  scale_fill_gradient2(low='blue', midpoint=0, high='red', limits=c(-3,3)) + 
  ggtitle(sprintf('Raw data %s', var)) + theme(legend.position="bottom", legend.key.width = unit(0.06, "npc"))
plot1 <- ggplot(NL) + geom_sf() + geom_sf(aes(fill=mean), data=terms.sf %>% filter(meta=="Uncertain")) + 
  scale_fill_gradient2(low='blue', midpoint=0, high='red', limits=c(-3,3)) + 
  ggtitle(sprintf('Joint Model %s', var)) + theme(legend.position="bottom", legend.key.width = unit(0.06, "npc"))
plot2 <- ggplot(NL) + geom_sf() + geom_sf(aes(fill=mean), data=terms.sf %>% filter(meta=="Certain")) + 
  scale_fill_gradient2(low='blue', midpoint=0, high='red', limits=c(-3,3)) + 
  ggtitle(sprintf('Two-Stage Model %s', var)) + theme(legend.position="bottom", legend.key.width = unit(0.06, "npc"))
plot4 <- ggplot(NL) + geom_sf() + geom_sf(aes(fill=sd), data=terms.sf %>% filter(meta=="Uncertain")) + 
  scale_fill_gradient(low='white', high='red', limits=c(0,max(terms.sf$sd))) + 
  ggtitle(sprintf('Joint Model %s', var)) + theme(legend.position="bottom", legend.key.width = unit(0.06, "npc"))
plot5 <- ggplot(NL) + geom_sf() + geom_sf(aes(fill=sd), data=terms.sf %>% filter(meta=="Certain")) + 
  scale_fill_gradient(low='white', high='red', limits=c(0,max(terms.sf$sd))) + 
  ggtitle(sprintf('Two-Stage Model %s', var)) + theme(legend.position="bottom", legend.key.width = unit(0.06, "npc"))
#plot.all <- plot_grid(plot0, plot1, plot2, NULL, plot4, plot5, nrow = 2) + theme(plot.background = element_rect(fill = "white", colour = NA))
plot.all <- ggdraw() +
  draw_plot(plot0, x = 0, y = .5, width = 0.33, height = .5) +
  draw_plot(plot1, x = 0.33, y = .5, width = 0.33, height = .5) +
  draw_plot(plot2, x = 0.66, y = .5, width = 0.33, height = .5) +
  draw_plot(plot4, x = 0.33, y = 0, width = 0.33, height = .5) +
  draw_plot(plot5, x = 0.66, y = 0, width = 0.33, height = .5) +
  draw_plot_label(label = c("A", "B", "C", "D", "E"), size = 15, x = c(0.00, 0.33, 0.66, 0.33, 0.66), y = c(1.00, 1.00, 1.00, 0.50, 0.50))
ggsave(sprintf('results_paper/species_%s.png', var), width=3200, heigh=3000, units='px')
ggsave(sprintf('results_paper/species_%s.tiff', var), width=3200, heigh=3000, units='px', compression="lzw")
}
```

@@

plot.scatter <- ggplot() + geom_point(aes(x=`Two-Stage Model`, y=`Joint Model`), data=terms.plot, size=0.1, alpha=0.2) + geom_abline() + 
     facet_wrap( ~ type + model, ncol = 3, scales="free") #+ ggtitle('Predicted Log-Odds (SDM) and \nPredicted Mean (Abiotics) at Grid Cells')
plot.scatter
ggsave('results_paper/species_scatter.png', width=1800, heigh=2400, units='px')
ggsave('results_paper/species_scatter.tiff', width=1800, heigh=2400, units='px', compression="lzw")
```

@@

```{r}
results <- read.csv("data_paper/results.csv")
```

@@

```{r}
# Linear terms for all species
terms.plot <- results %>% filter((term == "fixed") & (model == "SDM")  & (ID != "intercept")) %>% 
  mutate(ID=fct_relevel(ID, "ORG_STOF.z", "CN.z", "N_totaal.z", "P_totaal.z", "K_CaCl2.z")) %>% #"intercept",  
  mutate(meta=factor(recode(meta, "Certain" = "Two-Stage", "Uncertain"="Joint"), levels=c("Two-Stage", "Joint"))) %>%
  merge(species.map) %>% mutate(species = name)
plot.abiotics.all <- ggplot(terms.plot, aes(x=ID, y=mean, col=meta, group=meta)) + 
  geom_point(position=position_dodge(width=0.5), size=2) +
  geom_errorbar(position=position_dodge(width=0.5), aes(ymin=X0.025quant, ymax=X0.975quant)) +
  theme(legend.position="top", axis.text.x = element_text(angle = 90)) + 
  scale_color_discrete(name = "Model") +
  scale_x_discrete(name='Covariate') + 
  scale_y_continuous(name='Value') +coord_cartesian(ylim=c(-5,5))+ #ylim=c(-10,10)
  facet_wrap( ~ species, ncol = 5)#, scales="free"
plot.abiotics.all
ggsave('results_paper/all_abiotics.png', width=2400, heigh=4000, units='px')
ggsave('results_paper/all_abiotics.tiff', width=2400, heigh=4000, units='px', compression="lzw")
```

@@

ggplot(compare.cor, aes(x=cor)) + 
  geom_histogram(color="black", fill="white", breaks=seq(0.8,1.0,0.01)) + 
  ylab("Number of Species") +xlab("Pearson Correlation Coefficient") +
  facet_wrap( ~ model, ncol = 3)  #+ggtitle('Correlation between Certain vs. Uncertain Abiotic Model Predictions')
ggsave('results_paper/species_correlation.png', width=2000, heigh=1200, units='px')
ggsave('results_paper/species_correlation.tiff', width=2000, heigh=1200, units='px', compression="lzw")
```

@@

sf.grid$fgr <- factor(sf.grid$lmf_indeling, levels=c("afz", "duo", "duw", "hll", "hzn", "hzo", "hzv",
                                                     "hzz", "lvh", "lvn", "riv", "zkm", "zkn", "zkz"))
levels(sf.grid$fgr) <- list("Closed estuaries"="afz",
                         "Dunes mainland"="duo",
                         "Dunes Wadden islands"="duw",
                         "Tidal areas Wadden islands"="gtw",
                         "Tidal areas Zeeland"="gtz",
                         "Hill country Limburg"="hll",
                         "Higher sandy soils North"="hzn",
                         "Higher sandy soils East"="hzo",
                         "Higher sandy soils Veluwe"="hzv",
                         "Higher sandy soils South"="hzz",
                         "Low peat Holland"="lvh",
                         "Low peat North"="lvn",
                         "River area"="riv",
                         "Sea clay middle"="zkm",
                         "Sea clay North"="zkn",
                         "Sea clay South"="zkz")

colors = c("Closed estuaries"="#d62627",
           "Dunes mainland"="#ea6d6e",
           "Dunes Wadden islands"="#ffbfbf",
           "Tidal areas Wadden islands"="#1f77b4",
           "Tidal areas Zeeland"="#64a9d9",
           "Hill country Limburg"="#bfe4ff",
           "Higher sandy soils North"="#ff7f0e",
           "Higher sandy soils East"="#ffae66",
           "Higher sandy soils Veluwe"="#bfffbf",
           "Higher sandy soils South"="#ffddbf",
           "Low peat Holland"="#6acf6a",
           "Low peat North"="#2ca02c",
           "River area"="#00BFC4",
           "Sea clay middle"="#b88fde",
           "Sea clay North"="#9466bd",
           "Sea clay South"="#e0bfff")

ggplot(NL) + geom_sf() +
	geom_sf(aes(geometry=geometry.1, fill=fgr,linewidth=0.1,colour=""), data=sf.grid) +
  scale_linewidth_identity() +
  scale_fill_manual(values=colors, na.value='gray',na.translate = F,name='Physical Geological Region') +
  scale_colour_manual(values=NA) +
  guides(colour=guide_legend("Not mappable", override.aes=list(colour="gray"))) +
	theme(legend.position="right") + ggtitle('Physical Geographical Regions') 
ggsave('results_paper/fgr.png', width=2000, heigh=1400, units='px')
ggsave('results_paper/fgr.tiff', width=2000, heigh=1400, units='px', compression="lzw")

```{r}
prov_geom <- read_sf("data_paper/provincies.gpkg")$geom
prov_geom <- (prov_geom - matrix(data=c(155000, 463000), ncol=2)) * matrix(data=c(1/1000, 1/1000), ncol=2)
colors = c("#1f77b4","#aec7e8",
          "#ff7f0e","#ffba78",
          "#2ca02c","#98df8a",
          "#d62627","#ff9896",
          "#9466bd","#c5b0d5",
          "#8c564b","#c49c94")
names(colors) = c('Drenthe',
 'Flevoland',
 'Fryslân',
 'Gelderland',
 'Groningen',
 'Limburg',
 'Noord-Brabant',
 'Noord-Holland',
 'Overijssel',
 'Utrecht',
 'Zeeland',
 'Zuid-Holland')
ggplot() + 
	geom_sf(aes(geometry=geometry.1, fill=naam,linewidth=0.1), data=sf.grid) +
  geom_sf(aes(geometry=prov_geom),fill=NA) +
  scale_linewidth_identity() +
  scale_fill_manual(values=colors, na.value='gray',name='Province') +
  theme(legend.position="right") +ggtitle('Provinces of the Netherlands')  
ggsave('results_paper/provinces.png', width=1700, heigh=1200, units='px')
ggsave('results_paper/provinces.tiff', width=1700, heigh=1200, units='px', compression="lzw")
